Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-09-04 Manuscript.Rmd
Added a bit on Seed-FC methods

### *Seed-based FC vs Community Detection*
### *Structural Characteristics*

>>>>

### *Seed-based FC vs Community Detection*

A potential downfall of the present approach is that it can be computationally demanding, while more direct seed-based functional connectivity methods could provide sufficient approximations of an individual's DMN orgnization. We examined this issue by estimating mPFC functional maps from its vertex-wise functional coupling with the mean PCC activation. For each subject, we computed the mean time series of all vertices contained within the PCC region of a standard DMN arrangement [@Yeo2011], and correlated it (Pearons) with the time series of every mPFC vertex from our ROIs.

### *Structural Characteristics*
